\chapter{Preparing the Experiment}

\section{Objective}

To study projectile motion in real life, considering the effects of air resistance. 

\section{Theory}

\subsection{Projectile Motion without Air Resistance}

The motion of an object thrown into the air is called projectile motion. Neglecting air resistance, the projectile follows a parabolic path due to the constant acceleration of gravity. The equations of motion for projectile motion are:

\begin{equation}
    \begin{split}
        x(t) &= v_{0} \cdot \cos(\theta) \cdot t \\
        y(t) &= v_{0} \cdot \sin(\theta) \cdot t - \frac{1}{2} g t^2 \\
    \end{split}
\end{equation}

\noindent where:

\begin{itemize}
    \item $x(t)$ and $y(t)$ are the horizontal and vertical positions of the projectile at time $t$.
    \item $v_{0}$ is the initial velocity of the projectile.
    \item $\theta$ is the launch angle.
    \item $g$ is the acceleration due to gravity (approximately $9.81 \, m/s^2$).
    \item $t$ is the time of flight.
\end{itemize}

\subsection{Projectile Motion with Air Resistance}

In the presence of air resistance, the projectile experiences an additional force that opposes its motion. This force is proportional to the speed of the projectile and acts in the opposite direction of the projectile's velocity. The equations of motion for projectile motion with air resistance are more complex and cannot be solved analytically.

\newpage
\thispagestyle{plain}

Experimental Procedure:

\begin{itemize}
    \item Set up the spring gun at an angle $\theta$ with the horizontal.
    \item Measure the distance $R$ from the gun to the point where the ball lands. 
    \item Measure the height $H$ of the highest point reached by the ball. 
    \item Repeat steps 1--3 for different initial angles $\theta$. 
    \item Calculate the average initial velocity $v_0$ of the ball by firing the gun horizontally and measuring the distance it travels. 
    \item Measure the mass $m$ of the ball.
    \item Compare the theoretical and experimental results for $R$, $H$, and $\theta$. Discuss the effects of air resistance on the trajectory of the projectile. 
\end{itemize}
